---
title: "Linear Analysis"
output: html_notebook
---

```{r}
df = read.csv("~/Desktop/New_South_Wales/Japan_Project/data/Japan_Visitor_Data.csv")
```

``` {r}
period = 24

length = dim(df)[1]

df_train = df[1:(length - period),]
x_train = ts(df_train$Daily_Visitors, start = c(1996,1), frequency = 12)
df_test = df[((length - period)+1):length,]
y <- ts(df_test$Daily_Visitors,
        start = c(2024, 2),   # Feb 2024
        frequency = 12)

options(scipen = 999) # Turns off scientific notation
```

ets - no trend, no seasonality. Just a prediction based on the weighted average of past results. 

```{r}
library(forecast)
model = ets(x_train, model = "ANN")
fc_ANN = forecast(model, h = 24)
```

```{r}
plot(fc_ANN)
#accuracy(fc_ANN, y)
```
Next we are gonna forecast assuming a trend but with dampening (so the trend decreases over time)

```{r}
model = ets(x_train, model = "AAN", damped = TRUE)
fc_AAdN = forecast(model, h = 24)
```

```{r}
plot(fc_AAdN)
#accuracy(fc_AAdN, y)
```

Now, we are going to forecast with both a multiplicative trend and a seasonal period of every 12 months

```{r}
y = ts(x_train, frequency = 12) # Setting the frequency - Once every 12 months
model = ets(y, model = "MAM")
fc_MAM = forecast(model, h = 24)
plot(fc_MAM, ylab = "Visitors", xlab = "Year")
#accuracy(fc_AAdN$mean, df_test$Daily_Visitors)
```

The error bars were way too big (possibly owing to the COVID pandemic making the mulitplicitive analysis too severe), so I'm going to try additive seasonality. 
```{r}
model = ets(x_train, model = "AAA")
fc_AAA = forecast(model, h = 24)
plot(fc_AAA, ylab = "Visitors", xlab = "Year")
lines(df_test$Daily_Visitors, col = "black", lwd = 2)
print(fc_AAA)
```

This looks much more reasonable

